User-level Grid Monitoring with Inca 2

### 2007-04-16 papers/hpdc-gmw-2007/paper.tex
modification to add industry tools
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6852 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

% What types of Grid monitoring are around and what the limitations are
One approach to monitoring Grids, used by tools such as
MonALISA~\cite{monalisa} and GridICE~\cite{gridice}, is to aggregate and
display data from existing cluster or system administrator monitoring tools
such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, or
Nagios~\cite{nagios}.  This provides a centralized, systems-level view of Grid
resources where low-level host statistics and queue information can be
examined.  This type of monitoring information is useful for showing the
utilization of Grid resources, but it does not provide the type of
high-level monitoring needed to detect user problems, such as incompatible
software versions, within the Grid infrastructure.

% What user-level monitoring provides and why we think it is good
User-level Grid monitoring provides Grid infrastructure testing and performance measurement 
from a generic, impartial user's perspective.  The goal of user-level monitoring is 
to detect and fix Grid infrastructure problems before users notice them -- 
user complaints should not be the first indication of Grid failures.  
In our view, a successful user-level Grid monitoring system needs to include
these features:

@@

To begin reporter configuration, the Inca administrator enters the location of
one more reporter repositories, and incat loads and displays the reporters
available from them (Figure~\ref{incat_fig}).
For each reporter, the Inca administrator can specify the resources to run on,
input arguments, the runtime environment, the frequency of execution, resource
limits, and email notifications.  The sequence of reports that a reporter
produces on a resource when executed with specific set of input arguments and
runtime environment is known as a \emph{report series} (or \emph{series} for
short).
Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
produce one report series when executed with 'blue.ufo.edu' as the host argument and another report series with 'red.ufo.edu'.  A set of related
series can be grouped into \emph{suites} and shared across other Inca
deployments, e.g.,  a Globus suite or a data transfer
performance suite.  Suites can also be useful in determining interoperability
among Grids or whether an application's requirements are being
fulfilled on a Grid.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
The depot provides full archiving of reporter output, and the database schema is
tuned to minimize redundant data.  Inca administrators can specify comparison
tests to run on reports as they are received, and the depot will send email
when the results of these tests change.  This provides the administrator
with quick notification of problems as they appear and of the results of
repairs.

@@

Other Inca users include the European DEISA Grid~\cite{deisa} and the UK National Grid
Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005 respectively.  
Similar to TeraGrid, DEISA uses Inca to verify their Common
Production Environment (DCPE) across 11 heterogeneous resources.  They
currently have 40 version reporters to verify each of the packages included in
DCPE.  In addition, they have unit reporters for the DEISA Applications Test
Suite (DATS) to check basic operation of the C/C++/Fortran compilers, the MPI
library, some numerical libraries, OpenMP jobs, CORBA middleware, and a third
party application.  DEISA is currently using Inca 1 and will transition to
Inca 2 in the next few months.

@@

Also to aid system administrator troubleshooting,
we plan to enhance Inca with a knowledge base that can be used to
discuss problems and suggest solutions.
The knowledge base will be populated by solutions provided by
system administrators, self-moderated to
improve quality.
This knowledge base could provide a vital resource
for system administrators and offer a forum for sharing
valuable experience and skills.

>>>>

% What types of Grid monitoring are around and what the limitations are
One approach to monitoring Grids, used by tools such as
MonALISA~\cite{monalisa} and GridICE~\cite{gridice}, is to aggregate and
display data from existing cluster or system administrator monitoring tools
such as Ganglia~\cite{ganglia}, CluMon~\cite{clumon}, or
Nagios~\cite{nagios}.  This provides a centralized, systems-level view of Grid
resources where low-level host statistics and queue information can be
examined.  This type of monitoring information is useful for showing the
utilization of Grid resources, but it does not provide the type of
high-level monitoring needed to detect user problems, such as incompatible
software components, within the Grid infrastructure.  Industry monitoring
tools are also available such as IBM Tivoli Monitoring~\cite{tivoli} and
Microsoft Operations Manager~\cite{mom}, which monitor and manage large
networks of services.  However, these tools depend on proprietary software and
are targeted to a single administrative domain, which is unsuitable for Grid
systems that span multiple administrative domains.

% What user-level monitoring provides and why we think it is good
User-level Grid monitoring provides Grid infrastructure testing and performance measurement 
from a generic, impartial user's perspective.  The goal of user-level monitoring is 
to detect and fix Grid infrastructure problems before users notice them by
notifying site system administrators and providing them with the error details -- 
user complaints should not be the first indication of Grid failures.  
In our view, successful user-level Grid monitoring needs to include
these features:

@@

To begin reporter configuration, the Inca administrator enters the location of
one more reporter repositories, and incat loads and displays the reporters
available from them (Figure~\ref{incat_fig}).
For each reporter, the Inca administrator can specify the resources to run on,
input arguments, the runtime environment, the frequency of execution, resource
limits, and email notifications.  The sequence of reports that a reporter
produces on a resource when executed with a specific set of input arguments and
runtime environment is known as a \emph{report series} (or \emph{series} for
short).
Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
produce one report series when executed with 'blue.ufo.edu' as the host argument and another report series with 'red.ufo.edu'.  A set of related
series can be grouped into \emph{suites} and shared across other Inca
deployments, e.g.,  a Globus suite or a data transfer
performance suite.  Suites can also be useful in determining interoperability
among Grids or whether an application's requirements are being
fulfilled on a Grid.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
The depot provides full archiving of reporter output, and the database schema is
tuned to minimize redundant data.  Inca administrators can specify pattern
tests to run on reports as they are received, and the depot will send email
when the results of these tests change.  This provides the administrator
with quick notification of problems as they appear and of the results of
repairs.

@@

Other Inca users include the European DEISA Grid~\cite{deisa} and the UK National Grid
Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005, respectively.  
Similar to TeraGrid, DEISA uses Inca to verify their Common
Production Environment (DCPE) across 11 heterogeneous resources.  They
currently have 40 version reporters to verify each of the packages included in
DCPE.  In addition, they have unit reporters for the DEISA Applications Test
Suite (DATS) to check basic operation of the C/C++/Fortran compilers, the MPI
library, some numerical libraries, OpenMP jobs, CORBA middleware, and a third
party application.  DEISA is currently using Inca 1 and will transition to
Inca 2 in the next few months.

@@

Also to aid system administrator troubleshooting,
we plan to enhance Inca with a knowledge base that can be used to
discuss problems and suggest solutions.
The knowledge base will be populated by solutions provided by
system administrators and self-moderated to
improve quality.
This knowledge base could provide a vital resource
for system administrators and offer a forum for sharing
valuable experience and skills.
